### 2023-04-06 paper-reviews/papers-2023.tex
Add MARSS reference

    The article describes an approach for fast full-system cycle-accurate simulation to enable efficient hardware and software co-design. The approach address fixed-software limitation of the standard checkpoint-based critical path cycle-accurate simulation approach. First, the authors reduced the porting of functional warming for the samples and introduced error estimation algorithm for cache warming. The error estimation compares best- and worst-case results (run in parallel) to determine whether limited functional warming has significant effect on the results or not. The technique is named Full Speed Ahead. The authors extended the technique with parallel sample execution. The main idea of the parallel Full Speed Ahead approach is to break target workload into samples and execute the samples in parallel while fast-forwarding to the sample boundaries using hardware-supported virtualization. As result, the authors claims to achieve near-native simulation speed while running on a wide enough (in terms of processor cores) host systems.
\end{itemize}

>>>>

    The article describes an approach for fast full-system cycle-accurate simulation to enable efficient hardware and software co-design. The approach address fixed-software limitation of the standard checkpoint-based critical path cycle-accurate simulation approach. First, the authors reduced the porting of functional warming for the samples and introduced error estimation algorithm for cache warming. The error estimation compares best- and worst-case results (run in parallel) to determine whether limited functional warming has significant effect on the results or not. The technique is named Full Speed Ahead. The authors extended the technique with parallel sample execution. The main idea of the parallel Full Speed Ahead approach is to break target workload into samples and execute the samples in parallel while fast-forwarding to the sample boundaries using hardware-supported virtualization. As result, the authors claims to achieve near-native simulation speed while running on a wide enough (in terms of processor cores) host systems.

    \item \cite{Patel:MARSS:2011}:

    The article is about Micro Architectural and System Simulator (MARSS). The simulator is constructed as a combination of QEMU and PTLSim. PTLSim and QEMU share the same processor structure which allows them to switch seamlessly thus providing a gear-shit capability for mixing functional and cycle-accurate execution. QEMU provides all the peripherals in the setup. The article uses term emulation for function models and simulation for cycle-accurate models. This is another view on this controversial topic that can be a reference for the \href{https://github.com/yulyugin/sim-lectures}{<<Fundamentals of Full-Platform Simulation>>} course.
\end{itemize}
